supplmental

### 2020-01-01 supplement.Rmd
big update

---
title: "supplmental"
output: html_document
---

@@

  library(tidyverse)
  source("scripts/functions.R")
  load("scripts/models_july_2019.RData")

  library(sjPlot)

@@

Table 3. Mixed-effects model estimates for systolic blood pressure (mmHg)

@@

S-Table 1. Mixed-effects model estimates for diastolic blood pressure (mmHg)

@@

S-Table 2. Mixed-effects model estimates for oscillatory systolic blood pressure (mmHg)
```{r}

# OCS SBP

  tab_model(
    me_osc_sbp, me_osc_sbp_p, me_osc_sbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_osc_sbp.html",
    pred.labels = c(labs, "OSC SBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

S-Table 3. Mixed-effects model estimates for oscillatory diastolic blood pressure (mmHg)

# OCS DBP

  tab_model(
    me_osc_dbp, me_osc_dbp_p, me_osc_dbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_osc_dbp.html",
    pred.labels = c(labs, "OSC DBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

S-Table 4. Mixed-effects model estimates for central systolic blood pressure (mmHg)

@@

S-Table 5. Mixed-effects model estimates for central diastolic blood pressure (mmHg)

@@

S-Table 6. Mixed-effects model estimates for OXLDL

```{r}
# OXLDL ####

@@

S-Table 7. Mixed-effects model estimates for arterial stiffness

@@

S-Table 8. Mixed-effects model estimates for fasting glucose

@@

S-Table 9. Mixed-effects model estimates for LDL

@@

S-Table 10. Mixed-effects model estimates for HDL

@@

S-Table 11. Mixed-effects model estimates for total cholesterol

@@

S-Table 12. Mixed-effects model estimates for TAG

@@

S-Table 13. Mixed-effects model estimates for PWA augment

@@

>>>>

---
title: ''
author: ''
date: ''
output: 
  html_document:
    df_print: paged
    keep_md: true
  word_document:
    reference_docx: style.1.docx
---

@@

# load("scripts/models_dec_2019.RData")
  source("scripts/01_project.R") # Produces the model and data objects

  library(sjPlot)
  library(tidyverse)

@@

Mixed-effects model estimates for systolic blood pressure (mmHg)

@@

Mixed-effects model estimates for diastolic blood pressure (mmHg)

@@

Mixed-effects model estimates for central systolic blood pressure (mmHg)

@@

Mixed-effects model estimates for central diastolic blood pressure (mmHg)

@@

Mixed-effects model estimates for log(OXLDL)

# OXLDL ####

@@

Mixed-effects model estimates for arterial stiffness

@@

Mixed-effects model estimates for fasting glucose

@@

Mixed-effects model estimates for LDL

@@

Mixed-effects model estimates for log(HDL)

@@

Mixed-effects model estimates for log(total cholesterol)

@@

Mixed-effects model estimates for log(TAG)

@@

Mixed-effects model estimates for PWA augment

@@

```{r hdl_variance_plot}

  mutate(hdl, tx = factor(tx, labels = c("Control", "Active"))) %>%
  filter(!is.na(ep)) %>%
  ggplot(aes(x = log(ep), fill = tx)) +
    geom_density(alpha = 0.5, color = "black") +
    theme_minimal() +
    xlab("HDL") +
    ylab("Density") +
    scale_fill_brewer("", palette = "Set1")

```{r all_distributions}

  dist(sbp, "SBP (mmHg)", logged = "no")

  dist(dbp, "DBP (mmHg)", logged = "no")

  dist(art_stif, "Arterial Stiffness", logged = "no")

  dist(glu, "Glucose", logged = "no")

  dist(hdl, "HDL", logged = "no")
  dist(hdl, "Log(HDL)", logged = "yes")

  dist(ldl, "LDL", logged = "no")

  dist(oxldl, "OXLDL", logged = "no")
  dist(oxldl, "Log(OXLDL)", logged = "yes")

  dist(pwa_augment, "PWA Augment", logged = "no")

  dist(tag, "TAG", logged = "no")
  dist(tag, "Log(TAG)", logged = "yes")

  dist(tchol, "TCHOL", logged = "no")
  dist(tchol, "Log(TCHOL)", logged = "yes")
